`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-09 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
incorporate color scheme into notebook

# infercnv files
infercnv_tsv <- file.path(
  infercnv_dir,
  glue::glue("{params$library_id}_cnv-metadata.tsv")
)
infercnv_png <- file.path(
  infercnv_dir,
  glue::glue("{params$library_id}_infercnv.png")
)
```

@@

# Read ewings cell types
celltype_df <- readr::read_tsv(ewings_tsv)
```

@@

```{r}
query_only_df <- library_has_cnv_df |>
  dplyr::filter(cell_group == "unknown") |>
  # create a finer cell type column for this plot
  dplyr::mutate(
    celltype_fine = dplyr::case_when(
      cell_group == "reference" ~ "reference cell",
      stringr::str_detect(ewing_annotation, "tumor") ~ "tumor cell",
      .default = ewing_annotation
    )
  ) |>
  dplyr::add_count(celltype_fine, name = "celltype_fine_count") |>
  dplyr::mutate(
    celltype_fine_n = glue::glue("{celltype_fine} (n={celltype_fine_count})"),
    # top 10 only
    celltype_fine_n = forcats::fct_lump(celltype_fine_n, 10),
  )

@@

# 11 hex colors!
# adapted from 'Classic 10' from paletteer: https://r-graph-gallery.com/color-palette-finder
colors <- c("#1F77B4", "#FF7F0E", "#2CA02C", "#D6272F", "#9467BD", "#8C564B", "#E377C2", "#7F7F7F", "#BCBD22", "#17CFFB", "#17CF1F")
```

>>>>

# infercnv files
infercnv_tsv <- file.path(
  infercnv_dir,
  glue::glue("{params$library_id}_cnv-metadata.tsv")
)
infercnv_png <- file.path(
  infercnv_dir,
  glue::glue("{params$library_id}_infercnv.png")
)

# celltype palette file
palette_file <- file.path("palettes", "SCPCP000015_palette.tsv")
```

@@

# Read ewings cell types and colors
celltype_df <- readr::read_tsv(ewings_tsv)
colors_df <- readr::read_tsv(palette_file)
```

@@

```{r}
query_only_df <- library_has_cnv_df |>
  dplyr::filter(cell_group == "unknown") |>
  # create a finer cell type column for this plot
  dplyr::mutate(
    celltype_fine = ifelse(
      stringr::str_detect(ewing_annotation, "tumor"),
      "tumor",
      ewing_annotation
    )
  ) |>
  dplyr::add_count(celltype_fine) |>
  dplyr::mutate(
    celltype_fine_n = glue::glue("{celltype_fine} (n={n})"),
    # top 10 only
    celltype_fine_n = forcats::fct_lump(celltype_fine_n, 10)
  )

@@

# Create color palette with (n=) in labels
color_n_df <- query_only_df |>
  dplyr::select(celltype_fine, celltype_fine_n) |>
  dplyr::inner_join(
    colors_df,
    by = c("celltype_fine" = "celltype")
  ) |>
  dplyr::select(celltype_fine_n, color) |>
  unique()
colors <- color_n_df$color
names(colors) <- color_n_df$celltype_fine_n

# Add in the other color with its label, since that won't be in the palette
colors[updated_other] <- "#D2D2D2"
```
